Appendix for: Deep Reinforcement Learning for Conservation Decisions

### 2021-04-28 manuscript/presubmission-letter.Rmd
Minor clarification edit

Advances in both available data and computing power have begun to open the door to a greater role for machine learning (ML) in addressing some of our planet's most pressing environmental problems, such as the growing frequency and intensity of wildfire, over-exploited fisheries, declining biodiversity, and zoonotic pandemics. 
But will ML approaches really help us tackle a changing planet?
Applications of ML in ecology have begun to illustrate the promise of both supervised learning (e.g. image recognition) and unsupervised learning (including clustering and prediction), but have so far largely overlooked the third and possibly most promising approach in the ML triad: Reinforcement Learning (RL).
Supervised and unsupervised learning approaches often require massive amounts of historical data to learn underlying patterns.
Even when such data is eventually available, they may prove reliable for relatively static tasks such as species identification from audio or visual recordings, yet be a poor guide to a future climate we have never observed.  
The task of selecting actions in an uncertain and changing environment to maximize some objective is the explicit focus of RL.

>>>>

Advances in both available data and computing power have begun to open the door to a greater role for machine learning (ML) in addressing some of our planet's most pressing environmental problems, such as the growing frequency and intensity of wildfire, over-exploited fisheries, declining biodiversity, and zoonotic pandemics. 
But will ML approaches really help us tackle a changing planet?
Applications of ML in ecology have begun to illustrate the promise of both supervised learning (e.g. image recognition) and unsupervised learning (including clustering and prediction), but have so far largely overlooked the third and possibly most promising approach in the ML triad: Reinforcement Learning (RL).
Supervised and unsupervised learning approaches often require massive amounts of historical data to learn underlying patterns.
Even when such data is eventually available, these two methods may prove reliable for relatively static tasks such as species identification from audio or visual recordings, yet be a poor guide to a future climate we have never observed.  
The task of selecting actions in an uncertain and changing environment to maximize some objective is the explicit focus of RL.
